---
title: "Exam_3"
output: html_document
code_folding: hide
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
div.blue { background-color:#63a898; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">



<style>
div.blue { background-color:#63a898; border-radius: 0px; padding: 20px;}
</style>
<div class = "blue">


## [HOME](http://AR-Polyhedron.github.io/) | [ABOUT ME](http://AR-Polyhedron.github.io/About_Me/) | [CV](http://AR-Polyhedron.github.io/CV/) | [PROGRAMMING](http://AR-Polyhedron.github.io/Programming/) | [RESEARCH](http://AR-Polyhedron.github.io/Research/) 

### [Data_Course](https://github.com/AR-Polyhedron/Data_Course_RAAB) [Exam 3](http://AR-Polyhedron.github.io/Exam_3/) | [Final](http://AR-Polyhedron.github.io/Final_Project/) 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(modelr)
library(broom)
library(dplyr)
library(fitdistrplus)
library(tidyr)
library(tidyverse)
#Loading my libraries
```

### Loading the data in and taking in a summarry and getting a feel for the data, as if it is the first time playing with it.

```{r}
df <- mtcars
summary(mtcars)
class(df$mpg)
class(df$cyl)
class(df$disp)
class(df$hp)
class(df$drat)
class(df$wt)
class(df$qsec)
class(df$vs)
class(df$am)
class(df$gear)
class(df$carb)
```

### Visualizing the data

```{r}
ggplot(df,aes(y=mpg, x=cyl)) + geom_point()
ggplot(df,aes(y=mpg, x=disp)) + geom_point()
ggplot(df,aes(y=mpg, x=hp)) + geom_point()
ggplot(df,aes(y=mpg, x=drat)) + geom_point()
ggplot(df,aes(y=mpg, x=wt)) + geom_point()
ggplot(df,aes(y=mpg, x=qsec)) + geom_point()
ggplot(df,aes(y=mpg, x=gear)) + geom_point()
ggplot(df,aes(y=mpg, x=carb)) + geom_point()
```

### So I want to keep things interesting and not do the same stuff with mtcars we have always done. I will be looking at drat and qsec and since I know you want some tidying of data I will filter it out based on if it has a v shaped engine or not.

```{r}
df2 <- filter(df, vs == 0)
df3 <- filter(df, vs == 1)
ggplot(df2,aes(y=mpg, x=drat)) + geom_point()
ggplot(df2,aes(y=mpg, x=qsec)) + geom_point()
ggplot(df3,aes(y=mpg, x=drat)) + geom_point()
ggplot(df3,aes(y=mpg, x=qsec)) + geom_point()
plot(df2$mpg ~ df2$drat+df2$qsec)
plot(df3$mpg ~ df3$drat+df3$qsec)
plot(df2$mpg ~ df2$drat:df2$qsec)
plot(df3$mpg ~ df3$drat:df3$qsec)
```

### Making models of it all now along with getting some summaries of the models

```{r}
mod1 <- lm(mpg~drat+qsec, data = df2)
mod1.2 <- lm(mpg~drat:qsec, data = df2)
mod2 <- lm(mpg~drat+qsec, data = df3)
mod2.2 <- lm(mpg~drat:qsec, data = df3)
summary(mod1)
summary(mod1.2)
summary(mod2)
summary(mod2.2)
```

### Testing the models against the plots to see how well they fit

```{r}
plot(df2$mpg ~ df2$drat)
abline(mod1)
abline(mod1.2)
plot(df2$mpg ~ df2$qsec)
abline(mod1)
abline(mod1.2, col="Blue")
plot(df3$mpg ~ df3$drat)
abline(mod2)
abline(mod2.2, col="Blue")
plot(df3$mpg ~ df3$qsec)
abline(mod2)
abline(mod2.2, col="Blue")
```

### Whelp the only one that worked was mod2 on mpg ~ drat for the straight shaped engines. Lets see if making some models of just drat or qsec works.

```{r}
mod3 <- lm(mpg~drat, data = df2)
mod3.2 <- lm(mpg~qsec, data = df2)
mod4 <- lm(mpg~drat, data = df3)
mod4.2 <- lm(mpg~qsec, data = df3)
mod5 <- lm(mpg~drat/qsec, data = df2)
mod6<- lm(mpg~drat/qsec, data = df3)
summary(mod3)
summary(mod3.2)
summary(mod4)
summary(mod4.2)
summary(mod5)
summary(mod6)
```

### Going to visualize the new models and see if they are working

```{r}
plot(df2$mpg ~ df2$drat)
abline(mod3)
abline(mod3.2)
plot(df2$mpg ~ df2$qsec)
abline(mod3)
abline(mod3.2, col="Blue")
plot(df3$mpg ~ df3$drat)
abline(mod4)
abline(mod4.2, col="Blue")
plot(df3$mpg ~ df3$qsec)
abline(mod4)
abline(mod4.2, col="Blue")
plot(df2$mpg ~ df2$drat)
abline(mod5)
plot(df2$mpg ~ df2$qsec)
abline(mod5)
plot(df3$mpg ~ df3$drat)
abline(mod6)
plot(df3$mpg ~ df3$qsec)
abline(mod6)
```

### Well some of these are working at least.Looks like Mod3 for mpg~qsec of df2,Mod4 for mpg~drat of df3, mod4.2 for mpg~qsec of df3, mod6 for mpg~qsec of df3 all worked. So now to look at their accuracy with the residuals along with Mod2 for mpg ~ drat of df3

```{r}
mean(mod2$residuals^2)
mean(mod3$residuals^2)
mean(mod4$residuals^2)
mean(mod4.2$residuals^2)
mean(mod6$residuals^2)
```

### Smallest value is Mod3 which applied to mpg~qsec of df2 the next one being Mod2 for for mpg ~ drat of df3. So we will test out predictions on those for the data sets

```{r}
preds1 <- add_predictions(df2,mod3)
preds2 <- add_predictions(df3,mod2)
preds1[5:10,c(1,5)]
preds2[5:10,c(1,5,7)]
```

```{r}
df2.1 = data.frame(mpg = c(16.4,17.3,15.2,10.4,10.4,14.7),
                   drat = c(3.07,3.07,3.07,2.93,3.00,3.23))
predictions1 = predict(mod3, newdata = df2.1)

df3.1 = data.frame(mpg = c(22.8,19.2,17.8,32.4,30.4,33.9),
                   drat = c(3.92,3.92,3.92,4.08,4.93,4.22),
                   qsec = c(22.90,18.30,18.90,19.47,18.52,19.90))
predictions2 = predict(mod2, newdata = df3.1)


{plot(df2$mpg ~ df2$qsec)
points(x=df2.1$mpg,y=predictions1, col="Red")
abline(mod3)}

{plot(df3$mpg ~ df3$drat)
points(x=df3.1$mpg,y=predictions2, col="Red")
abline(mod2)}
```

### Well I still seem to be flubbing the end of building models. Model 3 got prediction values on there but no line. The Predictions at least close to actual points, one even being on top of another. Model 2 none of the predictions got on there but the line did. So I would say there are trends with V shaped engines being correllated with drat. Along with straight engines being correlated with drat and qsec. However due to the poor modeling no real conclusion can be made.